Distributed Version Control Systems

### 2010-06-07 laarsample.tex
Quité eso de que aparezca tantas veces UTN

\affiliation{
\dag Universidad Tecnol\'{o}gica Nacional, Facultad Regional Buenos Aires \\
{\ demianalonso@gmail.com} \\
\ddag Universidad Tecnol\'{o}gica Nacional, Facultad Regional Buenos Aires \\
{\ bbonanno@gmail.com} \\
\dag \dag Universidad Tecnol\'{o}gica Nacional, Facultad Regional Buenos Aires \\
{\ nicolascalligaro@gmail.com} \\
\ddag \ddag Universidad Tecnol\'{o}gica Nacional, Facultad Regional Buenos Aires \\
{\ nicolas.perez.santoro@gmail.com }
}

@@

\title{Distributed Version Control Systems}
\author{Demian Alonso$^{\dag }$, Bruno Bonnano$^{\ddag }$, Nicol\'{a}s Calligaro$^{\dag \dag }$ and Nicol\'{a}s Perez Santoro$^{\ddag \ddag }$}
\maketitle

>>>>

%\affiliation{
% \dag Universidad Tecnol\'{o}gica Nacional, Facultad Regional Buenos Aires \\
% {\ demianalonso@gmail.com} \\
% \ddag Universidad Tecnol\'{o}gica Nacional, Facultad Regional Buenos Aires \\
% {\ bbonanno@gmail.com} \\
% \dag \dag Universidad Tecnol\'{o}gica Nacional, Facultad Regional Buenos Aires \\
% {\ nicolascalligaro@gmail.com} \\
% \ddag \ddag Universidad Tecnol\'{o}gica Nacional, Facultad Regional Buenos Aires \\
% {\ nicolas.perez.santoro@gmail.com }
% }

\affiliation{
 \dag {\ demianalonso@gmail.com} \\
 \ddag {\ bbonanno@gmail.com} \\
 \dag \dag  {\ nicolascalligaro@gmail.com} \\
 \ddag \ddag  {\ nicolas.perez.santoro@gmail.com }
 }

@@

\title{Distributed Version Control Systems}
\author{Demian Alonso$^{\dag }$, Bruno Bonnano$^{\ddag }$, Nicol\'{a}s Calligaro$^{\dag \dag }$ and Nicol\'{a}s Perez Santoro$^{\ddag \ddag }$}
%\author{Demian Alonso, Bruno Bonnano, Nicol\'{a}s Calligaro and Nicol\'{a}s Perez Santoro}
\maketitle
